### 2025-01-24 our_article/MCM_article/article_file.tex
论文更新

        \textbf{Explanation}: Natural disasters are considered low-probability events in agricultural activities. To ensure the generalizability of the model, natural disasters should not be considered.
      \end{itemize}
        \subsection{Notations}
      % table
      \begin{table}[h]
        \centering
        % \caption{An example of a three-line table.}
        \begin{tabular}{cc}
          \toprule
          \rowcolor{customcolor!40} % 设置背景颜色
          Symbols & Description\\
          \midrule
          $\mathbf{X}$ & Vector $[N_w,N_c,N_p,N_b,N_B,C_{hc},C_{pc}]^T$,etc. \\
          $w$ & Subscription for weeds \\
          $c$ & Subscription for crops \\
          $p$ & Subscription for pest \\
          $bir$ & Subscription for birds \\
          $bat$ & Subscription for bats \\
          $hc$ & Subscription for herbicide \\
          $pc$ & Subscription for pesticide \\
          $C_i$ & Concentration of certain chemical \\
          $N_i$ & Numbers of certain species \\
          $\alpha$ & $abc$ \\
          \bottomrule
        \end{tabular}
        \label{tab:example}
      \end{table}

  \section{Models}
        % figure
    \begin{figure}[ht]
      \centering
      \includegraphics[width=0.5\linewidth]{images/energy_flow.png} % 替换为你的第一张图片路径
      \caption{Energy Flow}
      \label{fig:EnergyFlow}
    \end{figure}

>>>>

        \textbf{Explanation}: Natural disasters are considered low-probability events in agricultural activities. To ensure the generalizability of the model, natural disasters should not be considered.
      \end{itemize}
        \subsection{Notations}
      % table
      \begin{table}[H]
        \centering
        % \caption{An example of a three-line table.}
        \begin{tabular}{cc}
          \toprule
          \rowcolor{customcolor!40} % 设置背景颜色
          Symbols & Description\\
          \midrule
          $\mathbf{X}$ & Vector $[N_w,N_c,N_p,N_b,N_B,C_{hc},C_{pc}]^T$ to describe the system,etc. \\
          $wd$ & Subscription for weeds \\
          $crp$ & Subscription for crops \\
          $pst$ & Subscription for pest(who consumes crops) \\
          $ins$ & Subscription for other insects(who consume weeds) \\
          $bd$ & Subscription for small birds(herbivorous) \\
          $Bd$ & Subscription for huge birds(carnivorous) \\
          $bt$ & Subscription for bats \\
          $snk$ & Subscription for snake \\
          $frg$ & Subscription for frog \\
          $HC$ & Subscription for herbicide \\
          $PC$ & Subscription for pesticide \\
          $C_i$ & Concentration of certain chemical \\
          $N_i$ & Numbers of certain species \\
          $r_i$ & Natural growth gate of certain species\\
          $K_i$ & Carrying capacity of certain species\\
          $\alpha$ & The effect of chemical concentration on growth rate\\
          $\beta$ & Interspecific competition factor\\
          $\gamma$ & Activity of decomposer\\

          \bottomrule
        \end{tabular}
        \label{tab:example}
      \end{table}

  % \section{Models}
  %       % figure
  %   \begin{figure}[ht]
  %     \centering
  %     \includegraphics[width=0.5\linewidth]{images/energy_flow.png} % 替换为你的第一张图片路径
  %     \caption{Energy Flow}
  %     \label{fig:EnergyFlow}
  %   \end{figure}
